\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{sectsty}

\geometry{margin=0.65in}
\setlist[itemize]{left=0pt, itemsep=0pt}
\subsubsectionfont{\normalfont}

\begin{document}
\pagestyle{empty}

\begin{center}
  \section*{\LARGE Esteban Alejandro Mayorga Vidaurre} \\
  \href{mailto:mayorgae0722@gmail.com}{mayorgae0722@gmail.com} \quad | \quad +57~300~5482387 \quad | \quad Colombia
\end{center}

\hrule
\vspace{4pt}

% Professional Summary
\subsection*{Summary}
Systems Engineer and Full Stack Developer with a diverse background in mobile and web development, automation, and product management. Skilled in Flutter, Python, REST API integration, and cloud services, with proven experience in developing scalable solutions and optimizing internal processes. Passionate about leveraging modern architectures and agile methodologies to drive project success.

% Work Experience
\subsection*{Work Experience}

\subsubsection*{%
  \textbf{RPA and Application Developer} at \href{https://www.linkedin.com/company/qfdsolutions}{QFD solutions} working for \href{https://www.linkedin.com/company/arajet/}{Arajet}, Colombia
  \hfill
  \textit{November 2023 -- Present}
}
\begin{itemize}
  \item Developed RPA solutions and built reports to streamline internal processes.
  \item Modified stored procedures and constructed B2P systems.
  \item Deployed app services and functions on Azure.
\end{itemize}

\subsubsection*{%
  \textbf{Product Manager} at \href{https://startupslatam.com/planet-oliver-la-startup-colombiana-que-con-tecnologia-elimina-el-desperdicio-de-comida-alcanza-los-12-mil-usuarios/}{Planet Oliver}, Colombia
  \hfill
  \textit{October 2022 -- February 2024}
}
\begin{itemize}
  \item Led product management initiatives and provided development support using Flutter.
  \item Developed applications with Django and integrated REST APIs.
  \item Migrated architecture to microservices and deployed solutions to Azure AppServices with Docker.
\end{itemize}

\subsubsection*{%
  \textbf{Head of Development} at \href{https://www.linkedin.com/company/qfdsolutions/posts/?feedView=all}{QFD Solutions}, Colombia
  \hfill
  \textit{April 2022 -- October 2022}
}
\begin{itemize}
  \item Managed and led development teams.
  \item Provided development support using Flutter and integrated REST APIs.
\end{itemize}

\subsubsection*{%
  \textbf{Analyst Developer} at Anri, Colombia
  \hfill
  \textit{February 2022 -- April 2022}
}
\begin{itemize}
  \item Developed mobile applications with Flutter.
  \item Integrated REST APIs and built backend servers using Python and Django Rest Framework.
\end{itemize}

\subsubsection*{%
  \textbf{Mobile Analyst Developer} at \href{https://www.linkedin.com/company/agrofuturo/posts/?feedView=all}{Croper}, Colombia
  \hfill
  \textit{July 2021 -- February 2022}
}
\begin{itemize}
  \item Developed mobile applications with Flutter.
  \item Integrated REST APIs and implemented maps and dynamic forms.
\end{itemize}

\subsubsection*{%
  \textbf{Development Engineer} at \href{https://www.linkedin.com/company/comsatech/}{Comsatelites GPS}, Colombia
  \hfill
  \textit{March 2021 -- June 2021}
}
\begin{itemize}
  \item Automated processes and developed applications.
  \item Managed cloud servers using Azure instances.
\end{itemize}

% (Additional details available upon request)

% Education
\subsection*{Education}
\subsubsection*{\textbf{Systems Engineering} \hfill \textit{2022}}
\begin{itemize}
  \item Universidad Autónoma del Caribe, Colombia.
\end{itemize}

\subsubsection*{\textbf{Academic High School Diploma} \hfill \textit{2017}}
\begin{itemize}
  \item Colombia Colegio San Francisco.
\end{itemize}

% Skills
\subsection*{Skills}
\begin{itemize}
  \item \textbf{Languages:} C\#, Typescript, Dart, Python, SQL.
  \item \textbf{Mobile Development:} Advanced Flutter (Bloc, Riverpod, RxDart, GetX, Hive, SQLite, Clean Architecture), mobile app publishing.
  \item \textbf{Web Development:} REST API integration, Django, FastAPI, React and Next.js.
  \item \textbf{Automation \& Tools:} Selenium, tkinter, Pandas.
  \item \textbf{Cloud \& DevOps:} Azure, Docker, microservices, CI/CD.
  \item \textbf{Data \& Visualization:} SQL, structured databases, Power BI.
  \item \textbf{Methodologies:} UML, Agile (SCRUM).
  \item \textbf{Version Control:} Git.
\end{itemize}

% Languages Spoken
\subsection*{Languages}
\begin{itemize}
  \item Spanish: Native
  \item English: B2
\end{itemize}

\end{document}
